---
title: "479 Project"
author: "Zhengyun Dou"
date: "4/19/2018"
output: html_document
---

```{r,ewarning=F,message=F,results='hide'}
#list of required packages
library(devtools)
library(rvest)
library(tidyverse)
library(stringr)
library(quantmod) #financial package
library(twitteR) #twitter from R
library(rtweet)
library(base64enc) #supplementary package to the above
library(lubridate)
library(tidytext)
library(widyr)
library(igraph)
library(ggraph)
library(tm)
library(wordcloud)
library(wordcloud2)
library(Matrix)
library(rARPACK)
library(data.table)
library(tidyr)
library(sunburstR)
```

```{r}
data=tibble(company=c("American Outdoor Brands","Sturm, Ruger","Vista Outdoor","Olin"),
            symbol=c("AOBC","RGR","VSTO","OLN"),
            agency=c("NASDAQ","NYSE","NYSE","NYSE"))

getSymbols(data$symbol,from="2017-01-01",adjust=TRUE) #all the four companies  
stock=Cl(get(data$symbol[1])) #close column of AOBC
for(i in 2:length(data$symbol))
  stock=merge(stock,Cl(get(data$symbol[i]))) #closure stock price for all four companies     
colnames(stock)=data$symbol
# tail(stock)
stockchange=stock%>% diff
#head(stockchange)

plot(as.zoo(stockchange), screens = 1, lty = 1:3, xlab = "Date", ylab = "Difference")
legend("topleft", c("AOBC", "RGR", "VSTO","OLN"), lty = 1:3, cex = 0.5)
```

```{r}
mass=read_csv("Mother Jones' Investigation_ US Mass Shootings, 1982-2018 - US mass shootings.csv")
# from https://www.motherjones.com/politics/2012/12/mass-shootings-mother-jones-full-data/
# str(mass)
# head(mass)
mass2017=mass %>% 
  mutate(Date=mdy(mass$Date)) %>% 
  filter(Date>="2017-01-01") #covert the date to be the same format as in stock[]

mdays=function(a,x){
  day=matrix(nrow = x,ncol=length(a))
  for (i in 1:x){
    day[i,]=a+i}
  c(a,day)}
#create a function to extend the mass shooting date to the following x days

daterange1=mdays(mass2017$Date,7)
case=rep(1:14,c(6,6,6,2,5,6,5,6,3,6,5,5,5,6)) %>% as.tibble()

variance=stock[daterange1] %>% as.tibble() %>% 
  mutate(date=index(stock[daterange1])) %>%
  cbind(.,case) %>% rename(shootingcase=value) %>% 
  group_by(shootingcase) %>% 
  summarise(varianceAOBC=var(AOBC),varianceRGR=var(RGR),
            varianceVSTO=var(VSTO),varianceOLN=var(OLN)) %>% 
  mutate(date=sort(mass2017$Date)) %>% select(shootingcase,date,varianceAOBC:varianceOLN)

variance

stock$VSTO[mdays(ymd("2017-01-06"),7)]
stock$VSTO[mdays(ymd("2017-11-05"),7)]

stock[daterange1] %>% as.tibble() %>% 
  mutate(date=index(stock[daterange1])) %>%cbind(.,case) %>%  
  gather('AOBC','RGR','VSTO','OLN',key="Co",value="price") %>% 
  ggplot(aes(y=price,x=date))+
  geom_point()+
  facet_grid(Co~value)

stock%>% diff %>% .[mdays(ymd("2017-01-06"),7)]
stock%>% diff %>% .[mdays(ymd("2017-11-05"),7)]
```

```{r}
twitters=fread("gun_twitters.csv") %>% as.tibble()
#dim(twitters)
#head(twitters)

stop_words=rbind(stop_words,c("rt",""))
twitters$text=str_replace_all(twitters$text,"http[s].*","")
cleaned=twitters  %>% 
  select(text) %>% 
  unnest_tokens(word,text) %>% 
  anti_join(stop_words)

frequency=cleaned %>% 
  count(word,sort=TRUE) 

frequency %>% top_n(15)

wordcloud2(frequency,figPath = "gunman.jpg",size=10)
```


```{r}
cleaned_two=twitters%>% 
  select(text) %>% 
  unnest_tokens(words,text,token="ngrams",n=2) 

separated=cleaned_two %>% 
  separate(words,c("word1","word2"),sep=" ")

filtered=separated %>% 
  filter(!word1 %in% stop_words$word) %>% 
  filter(!word2 %in% stop_words$word) %>% 
  count(word1,word2,sort=TRUE)

#head(filtered)

filtered %>% filter(n>20) %>% 
  graph_from_data_frame() %>% 
  ggraph(layout="fr")+
  geom_edge_link(aes(edge_alpha=n,edge_width=n))+
  geom_node_point(color = "gray", size = 3) +
  geom_node_text(aes(label = name), vjust = 1.8, size = 3)

```
## The following part is for the volatility analysis. we build ARIMA model and extract the residuals from it. we regarded the $residual^2$ as the volatility.
## We choose AOBC, RGR, VSTO, OLN top four gun company stock adjusted price as our data. The data are all from 2017-01-03 to 2018-04-18.
## For the four company seems like they all have unit root and we need to take difference. 
## After differentiation the RGR and VSTO are already convert to stationary with no ACF and PACF in series. Thus we treated the diff.adjusted.price^2 as volatility.
## As for the rest two series which is AOBC, OLN. After differentiation we fited ARMA model to get the residuals and treated residuals^2 as volatility.

```{r}
library("aTSA")
library("TSA")
```

```{r}
#AOBC
getSymbols("AOBC") 
#acf(AOBC$AOBC.Adjusted,lag.max = 1000)
#pacf(AOBC$AOBC.Adjusted,lag.max = 1000)
#plot(AOBC$AOBC.Adjusted)
#unit root test
aTSA::adf.test(AOBC$AOBC.Adjusted); tseries::adf.test(AOBC$AOBC.Adjusted)
AOBC.Adjusted.diff<-diff(AOBC$AOBC.Adjusted)[-1]
par(mfrow=c(1,2))
#acf(AOBC.Adjusted.diff)
#pacf(AOBC.Adjusted.diff)
#Thus the original data in random walk
##
#eacf(AOBC.Adjusted.diff,ar.max=10,ma.max=10)
Box.test(AOBC.Adjusted.diff,type="Ljung-Box",lag=12)
#ARIMA(3,0,3)
#ARIMA(3,0,6)
#ARIMA(0,0,4)
m1<-arima(AOBC.Open.diff,order=c(3,0,3),include.mean = TRUE)
m2<-arima(AOBC.Open.diff,order=c(3,0,6),include.mean = TRUE)
m3<-arima(AOBC.Open.diff,order=c(0,0,6),include.mean = TRUE)
#confint(m1);tsdiag(m1)
#confint(m2);tsdiag(m2)
#confint(m3);tsdiag(m3)
Box.test(m1$residuals,lag=12,fitdf = 1,type="Ljung-Box")
Box.test(m2$residuals,lag=12,fitdf = 1,type="Ljung-Box")
Box.test(m3$residuals,lag=12,fitdf = 1,type="Ljung-Box")
m4<-arima(AOBC.Open.diff,order=c(0,0,6),include.mean = TRUE,fixed=c(0,0,0,NA,0,NA,0))
#confint(m4);tsdiag(m4)
Box.test(m4$residuals,lag=12,fitdf = 1,type="Ljung-Box")
resi_square<-m4$residuals^2
volatility<-xts(x = resi_square,order.by = index(AOBC.Open.diff))
index(volatility)[volatility[,1]>1]
plot(volatility,main="volatility of AOBC")
plot(AOBC.Adjusted.diff)
```

```{r}
#RGR
getSymbols("RGR") 
#acf(RGR$RGR.Adjusted)
#pacf(RGR$RGR.Adjusted)
#plot(RGR$RGR.Adjusted)
aTSA::adf.test(RGR$RGR.Adjusted); tseries::adf.test(RGR$RGR.Adjusted)
Box.test(RGR$RGR.Adjusted,type="Ljung-Box",lag=12)
RGR.Adjusted.diff<-diff(RGR$RGR.Adjusted)[-1]
par(mfrow=c(1,2))
#acf(RGR.Adjusted.diff)
#pacf(RGR.Adjusted.diff)
#eacf(RGR.Adjusted.diff)
Box.test(RGR.Adjusted.diff,type="Ljung-Box",lag=12)
plot(RGR.Adjusted.diff)
volatility<-xts(x=(RGR.Adjusted.diff-mean(RGR.Adjusted.diff))^2,order.by = index(RGR.Adjusted.diff))
plot(volatility,main="volatility of RGR")
```

```{r}
#VSTO
getSymbols("VSTO") 
VSTO.Adjusted<-VSTO$VSTO.Adjusted[!is.na(VSTO$VSTO.Adjusted)]
#acf(VSTO.Adjusted)
#pacf(VSTO.Adjusted)
#plot(VSTO.Adjusted)
aTSA::adf.test(VSTO.Adjusted); tseries::adf.test(VSTO.Adjusted)
Box.test(VSTO.Adjusted,type="Ljung-Box",lag=12)
VSTO.Adjusted.diff<-diff(VSTO.Adjusted)[-1]
par(mfrow=c(1,2))
#acf(VSTO.Adjusted.diff)
#pacf(VSTO.Adjusted.diff)
eacf(VSTO.Adjusted.diff)
Box.test(VSTO.Adjusted.diff,type="Ljung-Box",lag=12)
plot(VSTO.Adjusted.diff)
volatility<-xts(x=(VSTO.Adjusted.diff-mean(VSTO.Adjusted.diff))^2,order.by = index(VSTO.Adjusted.diff))
plot(volatility,main="volatility of VSTO")
```

```{r}
getSymbols("OLN") 
OLN.Adjusted<-OLN$OLN.Adjusted[!is.na(OLN$OLN.Adjusted)]
#acf(OLN.Adjusted)
#pacf(OLN.Adjusted)
aTSA::adf.test(OLN.Adjusted); tseries::adf.test(OLN.Adjusted)
Box.test(OLN.Adjusted,type="Ljung-Box",lag=12)
OLN.Adjusted.diff<-diff(OLN.Adjusted)[-1]
par(mfrow=c(1,2))
#acf(OLN.Adjusted.diff)
#pacf(OLN.Adjusted.diff)
eacf(OLN.Adjusted.diff)
Box.test(OLN.Adjusted.diff,type="Ljung-Box",lag=12)
m1<-arima(OLN.Adjusted.diff,order=c(4,0,4),include.mean = TRUE)#,fixed=c(0,0,0,NA,0,NA,0))
#confint(m1);tsdiag(m1)
m2<-arima(OLN.Adjusted.diff,order=c(4,0,4),include.mean = TRUE,fixed=c(0,NA,NA,0,0,NA,NA,0,0))
#confint(m2);tsdiag(m2)
Box.test(m1$residuals,type="Ljung-Box",lag=12)
Box.test(m2$residuals,type="Ljung-Box",lag=12)
par(mfrow=c(1,3))
#plot(OLN.Adjusted)
plot(OLN.Adjusted.diff)
volatility<-xts(x=m2$residuals^2,order.by = index(OLN.Adjusted.diff))
plot(volatility,main="volatility of OLN")
```
