---
title: "Untitled"
author: "Soyoung Kim"
date: "April 29, 2018"
output:
  rmarkdown::github_document: default
github_document: default

```{r}
library(devtools)
library(rvest)
library(tidyverse)
library(stringr)
library(quantmod) #financial package
library(twitteR) #twitter from R
library(rtweet)
library(base64enc) #supplementary package to the above
library(lubridate)
library(tidytext)
library(widyr)
library(igraph)
library(ggraph)
library(tm)
#library(wordcloud)
#library(wordcloud2)
library(Matrix)
library(rARPACK)
library(data.table)
library(tidyr)
#library(sunburstR)
library(aTSA)
library(TSA)
#library(topicmodels)
#library(NLP)


mass=read_csv("Mother Jones' Investigation_ US Mass Shootings, 1982-2018 - US mass shootings.csv")
# from https://www.motherjones.com/politics/2012/12/mass-shootings-mother-jones-full-data/
# str(mass)
# head(mass)
mass2017=mass %>% 
  mutate(Date=mdy(mass$Date)) %>% 
  filter(Date>="2017-01-01") #covert the date to be the same format as in stock[]

mass2017[,c(2,3,5,6)]


data=tibble(company=c("American Outdoor Brands","Sturm, Ruger","Vista Outdoor","Olin"),
            symbol=c("AOBC","RGR","VSTO","OLN"),
            agency=c("NASDAQ","NYSE","NYSE","NYSE"))

getSymbols(data$symbol,from="2017-01-01",adjust=TRUE) #all the four companies  
stock=Cl(get(data$symbol[1])) #close column of AOBC
for(i in 2:length(data$symbol))
  stock=merge(stock,Cl(get(data$symbol[i]))) #closure stock price for all four companies     
colnames(stock)=data$symbol
# tail(stock)
stockchange=stock%>% diff
#head(stockchange)

stock%>% as.tibble() %>% 
  mutate(date=index(stock))  %>%  
  gather('AOBC','RGR','VSTO','OLN',key="Co",value="price") %>% 
  ggplot(aes(y=price,x=date))+geom_line(aes(color=Co))


mdays=function(a,x){
  day=matrix(nrow = x,ncol=length(a))
  for (i in 1:x){
    day[i,]=a+i}
  c(a,day)}
#create a function to extend the mass shooting date to the following x days

daterange1=mdays(mass2017$Date,7)
case=rep(1:14,c(6,6,6,2,5,6,5,6,3,6,5,5,5,6)) %>% as.tibble()

```

``````{r fig.height=12, fig.width=12}
#adjusted the size of plot.
for_plot=stock[daterange1] %>% as.tibble() %>% 
  mutate(date=index(stock[daterange1])) %>%cbind(.,case) %>%  
  gather('AOBC','RGR','VSTO','OLN',key="Co",value="price") %>%
  `colnames<-`(c("date", "mass_shooting_case","company", "price"))






for_plot%>% ggplot(aes(y=price,x=date, color=company))+geom_point() +facet_wrap(~ mass_shooting_case, ncol = 4, scales = "free", labeller=label_both)+geom_line()+labs(title = "7 days of stock price change on the mass shooting events ")


```


